```{r}
link='https://github.com/ComputationalThinkingGroup5/Merge/raw/master/MergedData.csv'
# a RDS file from the web needs:
mergedFile=read.csv(link)
```

Verifying data structure:
```{r}
str(mergedFile,width = 50,strict.width='cut')
```


```{r}
# hypothesis 1: percentunemployment increases as percentbirthrate advances:
hypo1=formula(percentunemployment~ percentbirthrate)
# hypothesis 2: percentunemployment increases as percentbirthrate and pct_GDP_exp advance:
hypo2=formula(percentunemployment~ percentbirthrate * pct_GDP_exp)
```


```{r}
#
# results
gauss1=glm(hypo1,
           data = mergedFile,
           family = 'gaussian')

gauss2=glm(hypo2,
           data = mergedFile,
           family = 'gaussian')

```

3.See results:
·First Hypothesis
```{r}
summary(gauss1)
```
·Second Hypothesis
```{r}
summary(gauss2)
```
4.Search for better model:
```{r}
anova(gauss1,gauss2,test="Chisq")
```
Model for the first hypothesis is chosen. You can get the RSquared if needed:
```{r}
library(rsq)
rsq(gauss2,adj=T)
```
Finally, some nice summary plots:
You can see the coefficient estimates like this:
```{r}
library(dotwhisker)
```
```{r}
dwplot(gauss2,by_2sd = F)
```
You can also use margins library:
```{r}
library(margins)

cplot(gauss2,'percentbirthrate')
```
```{r}
cplot(gauss2,'pct_GDP_exp')
```
And the interaction:
```{r}
persp(gauss2)
```
Binary outcome
In this situation you have a binary dependent variable, which we do not currently have:
```{r}
mergedFile$percentunemploymentdico=ifelse(mergedFile$percentunemployment>median(mergedFile$percentunemployment,
                                        na.rm = T),
                      1,0)
```

Now we have it.

1.State hypothesis:
Let’s use the same ones:
```{r}
hypoDico1=formula(percentunemploymentdico~ percentunemployment)
hypoDico2=formula(percentunemploymentdico~ percentunemployment * pct_GDP_exp)
```
2.Reformat
```{r}
mergedFile$mergedFiledico=factor(mergedFile$percentunemploymentdico)
```

3.Compute regression models:
```{r}
Logi1=glm(hypoDico1,data = mergedFile,
          family = "binomial")
Logi2=glm(hypoDico2,data = mergedFile,
          family = "binomial")
```
4.See results:
·First Hypothesis:
```{r}
summary(Logi1)
```
3.Second Hypothesis:
```{r}
summary(Logi2)
```
5.Search for better model:
```{r}
lmtest::lrtest(Logi1,Logi2)
```
Model for the second hypothesis is chosen.

6.Logistics regression coefficients do not offer marginal effects on how much eah variable affects the probability of the ‘1’ outcome. We can get it using margins library:
```{r}
library(margins)
(marginsINFO = margins(Logi2))
```
In this case, I could produce a plot for both coefficients. Take a look at the summary of
```{r}
(marginsSUMM=summary(marginsINFO))
```
I can use that information like this:
```{r}
base= ggplot(marginsSUMM,
             aes(x=factor, y=AME))
base= base + geom_point()

plotMargins = base + theme(axis.text.x = element_text(angle = 80,size = 6,hjust = 1))
plotMargins    
```
We can add the the confidence intervals:
```{r}
plotMargins +  geom_errorbar(aes(ymin=lower,
                                 ymax=upper))
```
It is a good idea to use the indivual plots per variable:
```{r}
cplot(Logi2, "percentbirthrate")
```
```{r}
cplot(Logi2, "pct_GDP_exp")
```
And for the interaction:
```{r}
persp(Logi2)
```

